---
title: "27_04_23_Model_MH"
subtitle: "Modeling forecast count for MH"
execute: 
  message: false
  echo: true
  warning: false
  error: true

format: 
  html:
    self-contained: true
    code-line-numbers: true
    code-fold: true
    code-tools: true

custom_title_page: false
filters:
  - lightbox
lightbox: auto
---

### Log
> Version 2023-03-29.   
Code was initially made in SAS and send by ___Jemisha Apajee___. 
File Name: "Analysis_common_diseases_step_by_step_20221123.sas"

> Version 2023-04-19   
Translated to R by ___Javier Silva-Valencia___, adapted to Mental Health paper

> Version 2023-05-17   
Whitout social problems

> Version 2023-06-07   
Code debugged by **Percy Soto-Becerra**. The model's problem was fixed. Diagnostic regression assessment was performed.

### Context/Notes

- This is part of a mental health paper, where we are analyzing the amount of MH-related visits among several countries (countries part of INTREPID) in a pre and during pandemic period.

- The main variables are: Amount of total visits, amount of visits related to MH, 7-9 categories of MH groups, Tipe of visit(in-person, virtual) all this by month from 2018 to 2021 (Except Perú that has data from 2019-2021)

- ___This specific code___ is for creating a model that fits the time series and creating a forecast to compare prepandemic and pandemic trend.


## Getting ready

### Load packages

```{r,  results='hide', warning=FALSE, message = FALSE, collapse = TRUE}
if (!require("pacman")) install.packages("pacman")

pacman::p_load(rio, 
               here,
               tidyverse,
               purrr, 
               patchwork, 
               scales, 
               DT, 
               janitor, 
               lubridate, 
               gtsummary, 
               broom, 
               broom.mixed,
               ggeffects, 
               lme4, 
               nlme, 
               forecast, 
               MASS, 
               mgcv, 
               tsModel,
               zoo, 
               DHARMa, 
               patchwork,
               tsibble, 
               feasts, 
               qqplotr, 
               parameters, 
               flextable,
               stringr, 
               imputeTS)

source(here("source", "diag_glmm.R"))
source(here("source", "sti_plotter_pre.R"))
source(here("source", "sti_model.R"))
source(here("source", "sti_model_china.R"))
source(here("source", "sti_model_norway.R"))
source(here("source", "sti_model_usa.R"))
source(here("source", "sti_effect_ploter.R"))

# rm(list = ls())       #To clear the environment and start from zero.
# 
# Colors' palette
cbPalette <- c("#999999",  # 1
               "#E69F00",  # 2
               "#56B4E9",  # 3
               "#009E73",  # 4
               "#F0E442",  # 5
               "#0072B2",  # 6
               "#D55E00",  # 7
               "#CC79A7")  # 8 
```


### Read in data

```{r}
mh_visits <- import(here("Data", "All_countries_MHcounts.xlsx"), sheet = "MH_counts")
```

### View data structure

```{r}
datatable(head(mh_visits, 100))    #Seeing first 10 rows of the dataset
```


## Cleaning

### Creating variables

Create date:

```{r}
mh_visits <- mh_visits %>%
  mutate(date = as.Date(paste(month, "01", year), format = "%m %d %Y")) %>% 
  arrange(country, date)
```

Variables of interest for Mental Healht (MH) analysis

```{r}
# Select variable of interest
mh_visits1 <- mh_visits |> 
  dplyr::select(country, 
         mh_category,
         year,
         month,
         date,
         den_total, 
         total_counts, 
         in_person_counts, 
         virtual_counts, 
         period)

#Sorting
mh_visits1 <- mh_visits1 %>% 
  arrange(country, date, mh_category)

# Rename columns
mh_visits1 <- mh_visits1 %>%
  rename(numerator = total_counts,         #MH counts
         denominator = den_total)          #Total visits per month
```

### Check for missings

```{r}
mh_visits1 %>%
  tabyl(country, period, show_na = TRUE)           #No missings
```

### Sort categories of MH

```{r}
#Eliminando categorias eliminadas
mh_visits2 <- mh_visits1 %>% 
  filter(!(mh_category %in% c("Social Problems"))) 

# Establecer el nuevo orden para las categorías
new_order <- c("Anxiety and Mood Disorders", 
               "Bipolar, Schizophrenia and other Psycotic Disorders",
               "Dementia", 
               "ADHD and Eating Disorders", 
               "Sleep Disorders", 
               "Substance-Related and Addictive Disorders")

# Reorder categories
mh_visits2 <- mh_visits2 %>% 
  filter(mh_category %in% new_order) %>% 
  mutate(mh_category = fct_relevel(factor(mh_category), new_order))
```

###  Set up data for modelling

```{r}
pandemic_start       <- as.Date("2020-04-01")        #For all the countries the pandemic start april 2020 *To revise

pandemic_start_china <- as.Date("2020-02-01")  #For china pandemic start at feb 2020

mh_visits5           <- mh_visits2 %>%
  # create t = 1, ..., 48 for each country (except peru)
  mutate(
    tn = if_else(country != "Peru", 
                 (12 * (year - 2018)) + month, 
                 (12 * (year - 2019)) + month),
  time = tn, # for random effects in the residuals
  #Spliting N# visits into two variables (pre and post start of pandemic)   
  y_count = case_when(
    country != "China" & date < pandemic_start ~ numerator,
    country == "China" & date < pandemic_start_china ~ numerator,
    TRUE ~ NA_real_
    ),
  observed_count = case_when(
    country != "China" & date >= pandemic_start ~ numerator,
    country == "China" & date >= pandemic_start_china ~ numerator,
    TRUE ~ NA_real_
    ),
      
  # Dummy variables for China (changes in their health system administration)
  China_Jan19 = if_else(date >= as.Date("2019-01-01"), 1, 0),
  China_Dec20 = if_else(date >= as.Date("2020-12-01"), 1, 0),
  Norway_Feb21 = if_else(time >= 38, 1, 0), 
  USA_systdown = if_else(time >= 37 & time <= 39, 1, 0), 
  
  # Pre-post tag variable
  country = as.factor(country),
  pre_post = if_else(period == "pre-pandemic", 0, 1), 
  pre_postTo = if_else(is.na(y_count), "post", "pre"),      #pre/post binary variable
      
  #"tn" as a factor (will be a classification variable)
  tn = as.factor(tn), 
  
  #Creating variable for interaction pre-post exposure (wahsout would be on pre exposure)
  To = ifelse(period %in% c("pre-pandemic", "washout"), 0, 1), 
  
  # Creating rate variable for graphics
  rate = 10000 * numerator / denominator
  ) 

mh_visits_all <- mh_visits5 %>% 
  group_by(country, date) %>% 
  summarize(
    year = max(year),
    month = max(month),
    denominator = max(denominator),
    numerator = sum(numerator),
    observed_count = sum(observed_count),
    To = max(To), 
    time = max(time),
    period = max(period), 
    China_Jan19 = max(China_Jan19), 
    China_Dec20 = max(China_Dec20)
  ) %>%
  ungroup() |> 
  mutate(mh_category = "All common Mental Health disorders", 
         Norway_Feb21 = if_else(time >= 38, 1, 0), 
         USA_systdown = if_else(time >= 37 & time <= 39, 1, 0))

mh_visits_all  |> 
  bind_rows(mh_visits5) -> mh_visits5b
```

### Pre-pandemic behaviour of outcomes (blinded to post-pandemic)

```{r}
#| warning: false
#| message: false
min_tdate <- min(mh_visits5$date) #- month(1)
max_tdate <- max(mh_visits5$date) #+ month(1)

countryc <-  mh_visits5 |> 
  count(country) |> 
  pull(country) |> 
  as.character()

mh_categoryc <- mh_visits5 |> 
  count(mh_category) |> 
  pull(mh_category) |> 
  as.character()
```


```{r}
#| warning: false
#| message: false
combinations <- expand.grid(country = countryc, mh_category = mh_categoryc)

combinations <- combinations %>%
  mutate(plot = map2(country, mh_category, ~ 
                       sti_plotter_pre(.x, .y, 
                                       blind = FALSE, 
                                       data = mh_visits5))) %>%
  pwalk(~ ggsave(filename = paste0(..1, "_", ..2, ".png"), 
                 plot = ..3, 
                 device = "png", 
                 path = here("img", "exploratory_plots"), 
                 scale = 2, 
                 width = 7, 
                 height = 7, 
                 units = "cm", 
                 dpi = 900
                 ))

# Extrae la lista de gráficos
plots_list <- combinations$plot
```

::: {.panel-tabset}

### Anxiety/Mood

::: {.panel-tabset}

### Argentina

```{r}
i <- 1
plots_list[[i]]
```

### Australia

```{r}
i <- i + 1
plots_list[[i]]
```

### Canada

```{r}
i <- i + 1
plots_list[[i]]
```

### China

```{r}
i <- i + 1
plots_list[[i]]
```

### Norway

```{r}
i <- i + 1
plots_list[[i]]
```

### Peru

```{r}
i <- i + 1
plots_list[[i]]
```

### Singapore

```{r}
i <- i + 1
plots_list[[i]]
```

### Sweden

```{r}
i <- i + 1
plots_list[[i]]
```

### USA

```{r}
i <- i + 1
plots_list[[i]]
```

:::

### Bipolar/Schiz./Psycotic

::: {.panel-tabset}

### Argentina

```{r}
i <- i + 1
plots_list[[i]]
```

### Australia

```{r}
i <- i + 1
plots_list[[i]]
```

### Canada

```{r}
i <- i + 1
plots_list[[i]]
```

### China

```{r}
i <- i + 1
plots_list[[i]]
```

### Norway

```{r}
i <- i + 1
plots_list[[i]]
```

### Peru

```{r}
i <- i + 1
plots_list[[i]]
```

### Singapore

```{r}
i <- i + 1
plots_list[[i]]
```

### Sweden

```{r}
i <- i + 1
plots_list[[i]]
```

### USA

```{r}
i <- i + 1
plots_list[[i]]
```

:::

### Dementia


::: {.panel-tabset}

### Argentina

```{r}
i <- i + 1
plots_list[[i]]
```

### Australia

```{r}
i <- i + 1
plots_list[[i]]
```

### Canada

```{r}
i <- i + 1
plots_list[[i]]
```

### China

```{r}
i <- i + 1
plots_list[[i]]
```

### Norway

```{r}
i <- i + 1
plots_list[[i]]
```

### Peru

```{r}
i <- i + 1
plots_list[[i]]
```

### Singapore

```{r}
i <- i + 1
plots_list[[i]]
```

### Sweden

```{r}
i <- i + 1
plots_list[[i]]
```

### USA

```{r}
i <- i + 1
plots_list[[i]]
```

:::

### ADHD/Eating


::: {.panel-tabset}

### Argentina

```{r}
i <- i + 1
plots_list[[i]]
```

### Australia

```{r}
i <- i + 1
plots_list[[i]]
```

### Canada

```{r}
i <- i + 1
plots_list[[i]]
```

### China

```{r}
i <- i + 1
plots_list[[i]]
```

### Norway

```{r}
i <- i + 1
plots_list[[i]]
```

### Peru

```{r}
i <- i + 1
plots_list[[i]]
```

### Singapore

```{r}
i <- i + 1
plots_list[[i]]
```

### Sweden

```{r}
i <- i + 1
plots_list[[i]]
```

### USA

```{r}
i <- i + 1
plots_list[[i]]
```

:::

### Sleep


::: {.panel-tabset}

### Argentina

```{r}
i <- i + 1
plots_list[[i]]
```

### Australia

```{r}
i <- i + 1
plots_list[[i]]
```

### Canada

```{r}
i <- i + 1
plots_list[[i]]
```

### China

```{r}
i <- i + 1
plots_list[[i]]
```

### Norway

```{r}
i <- i + 1
plots_list[[i]]
```

### Peru

```{r}
i <- i + 1
plots_list[[i]]
```

### Singapore

```{r}
i <- i + 1
plots_list[[i]]
```

### Sweden

```{r}
i <- i + 1
plots_list[[i]]
```

### USA

```{r}
i <- i + 1
plots_list[[i]]
```

:::

### Substance-Related/Addictive


::: {.panel-tabset}

### Argentina

```{r}
i <- i + 1
plots_list[[i]]
```

### Australia

```{r}
i <- i + 1
plots_list[[i]]
```

### Canada

```{r}
i <- i + 1
plots_list[[i]]
```

### China

```{r}
i <- i + 1
plots_list[[i]]
```

### Norway

```{r}
i <- i + 1
plots_list[[i]]
```

### Peru

```{r}
i <- i + 1
plots_list[[i]]
```

### Singapore

```{r}
i <- i + 1
plots_list[[i]]
```

### Sweden

```{r}
i <- i + 1
plots_list[[i]]
```

### USA

```{r}
i <- i + 1
plots_list[[i]]
```

:::

:::

## Creating and Testing the Model

```{r}
# Countries and categories
countryc <-  mh_visits5b |> 
  count(country) |> 
  pull(country) |> 
  as.character()

countryc <- rep(countryc, 7)


mh_categoryc <- mh_visits5b |> 
  mutate(
    mh_category = 
      factor(mh_category, 
             levels = c("All common Mental Health disorders", 
                        "Anxiety and Mood Disorders", 
                        "ADHD and Eating Disorders", 
                        "Bipolar, Schizophrenia and other Psycotic Disorders", 
                        "Dementia", 
                        "Sleep Disorders", 
                        "Substance-Related and Addictive Disorders"))) |> 
  count(mh_category) |> 
  pull(mh_category) |> 
  as.character()
```

## Modelling

### Set global options

```{r}
# set options of graphics
alfa0 <- 0.5
alfa_ribbon0 <- 0.25
color_point0 <- c("#99B933")
color_line0 <- c("#002D72")
color_interrupt0 <- c("red")
color_ribbon_ex0 <- c("skyblue")
color_ribbon_def0 <- c("orange")
mindate0 <- "2018-01-01"
maxdate0 <- "2022-01-01"
```

### **Outcome:** All common Mental Health disorders

::: {.panel-tabset}

### Countries

1. Argentina
2. Australia
3. Canada
4. China
5. Norway
6. Peru
7. Singapore
8. Sweden
9. USA

### Argentina

```{r}
i <- 0
```

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1

if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 5, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0

tab0 |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot1

plot1
```

### Australia

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }

```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot2

plot2
```


### Canada

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot3

plot3
```


### China

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_china(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 2, q = 1, 
          data = mh_visits5b, 
          shock_exclude = FALSE)
```


- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot4

plot4
```

:::{.callout-important collapse=false appearance='default' icon=true}
## Notes
- Report in text (maybe in supplementary table?) that including period of shock (t > Dec 2020) does not significantly change the results.
:::


### Norway

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot5

plot5
```


### Peru

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 8, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot6

plot6
```

### Singapore

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }

```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot7

plot7
```

### Sweden

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot8

plot8
```


### USA

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }

```

```{r}
# Model
mod_full <- sti_model_usa(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot9

plot9
```
:::

#### Table

```{r}
# Cargar la biblioteca

tab_f <- tab |> 
  arrange(country, effect) |> 
  mutate(
    country_effect = if_else(effect == "Level change", country, NA_character_),
    effect = case_when(
      effect == "Level change" ~ "   Level change",
      effect == "Trend change" ~ "   Trend change"
    )
  ) |> 
  dplyr::select(-mh_category, -country) |> 
  dplyr::select(country_effect, effect, estimate)

# Crear la tabla flextable
ft <- flextable(tab_f)

# Cambiar los nombres de las columnas
ft <- set_header_labels(ft, 
                        country_effect = "Country",
                        effect = "Effect measure", 
                        estimate = "IRR (95%CI), p-value")

# Formatear la tabla
ft <- ft %>%
  align(align = "left") %>%
  padding(padding = 5) %>%
  fontsize(size = 11) %>%
  bold(part = "header") %>%
  bold(i = which(!is.na(tab_f$country_effect)), j = "country_effect") %>%
  autofit()

# Guardar como documento de Word
save_as_docx(ft, 
             path = here("table_effects", 
                         paste0("table_", mh_categoryc[j], ".docx")))

ft
```


#### Plot

```{r}
#| warning: false
#| message: false
((plot1 | plot2 | plot3) / 
  (plot4 | plot5 | plot6) / 
  (plot7 | plot8 | plot9)) + 
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A') & 
  theme(legend.position="bottom") -> plot_effect_final

ggsave(filename = paste0(mh_categoryc[j], ".png"), 
       plot = plot_effect_final, 
       device = "png", 
       path = here("img", "plot_effects"), 
       scale = 1.5, 
       width = 18, 
       height = 18, 
       units = "cm", 
       dpi = 900)
```

```{r}
knitr::include_graphics(here("img", 
                             "plot_effects", 
                             paste0(mh_categoryc[j], ".png")))
```


### **Outcome:** Anxiety and Mood Disorders

::: {.panel-tabset}

### Countries

1. Argentina
2. Australia
3. Canada
4. China
5. Norway
6. Peru
7. Singapore
8. Sweden
9. USA

### Argentina

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1

if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 5, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot1

plot1
```

### Australia

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot2

plot2
```


### Canada

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot3

plot3
```

### China

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_china(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 2, q = 1, 
          data = mh_visits5b, 
          shock_exclude = FALSE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot4

plot4
```

### Norway

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot5

plot5
```


### Peru

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 8, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot6

plot6
```

### Singapore

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }

```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot7

plot7
```

### Sweden

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot8

plot8
```

### USA

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_usa(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot9

plot9
```

:::

#### Table

```{r}
# Cargar la biblioteca

tab_f <- tab |> 
  arrange(country, effect) |> 
  mutate(
    country_effect = if_else(effect == "Level change", country, NA_character_),
    effect = case_when(
      effect == "Level change" ~ "   Level change",
      effect == "Trend change" ~ "   Trend change"
    )
  ) |> 
  dplyr::select(-mh_category, -country) |> 
  dplyr::select(country_effect, effect, estimate)

# Crear la tabla flextable
ft <- flextable(tab_f)

# Cambiar los nombres de las columnas
ft <- set_header_labels(ft, 
                        country_effect = "Country",
                        effect = "Effect measure", 
                        estimate = "IRR (95%CI), p-value")

# Formatear la tabla
ft <- ft %>%
  align(align = "left") %>%
  padding(padding = 5) %>%
  fontsize(size = 11) %>%
  bold(part = "header") %>%
  bold(i = which(!is.na(tab_f$country_effect)), j = "country_effect") %>%
  autofit()

# Guardar como documento de Word
save_as_docx(ft, 
             path = here("table_effects", 
                         paste0("table_", mh_categoryc[j], ".docx")))

ft
```


#### Plot

```{r}
#| warning: false
#| message: false
((plot1 | plot2 | plot3) / 
  (plot4 | plot5 | plot6) / 
  (plot7 | plot8 | plot9)) + 
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A') & 
  theme(legend.position="bottom") -> plot_effect_final

ggsave(filename = paste0(mh_categoryc[j], ".png"), 
       plot = plot_effect_final, 
       device = "png", 
       path = here("img", "plot_effects"), 
       scale = 1.5, 
       width = 18, 
       height = 18, 
       units = "cm", 
       dpi = 900)
```

```{r}
knitr::include_graphics(here("img", 
                             "plot_effects", 
                             paste0(mh_categoryc[j], ".png")))
```



### **Outcome:** ADHD and Eating Disorders

::: {.panel-tabset}

### Countries

1. Argentina
2. Australia
3. Canada
4. China
5. Norway
6. Peru
7. Singapore
8. Sweden
9. USA

### Argentina

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1

if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 5, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot1

plot1
```

### Australia

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot2

plot2
```


### Canada

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot3

plot3
```


### China

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_china(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 2, q = 1, 
          data = mh_visits5b, 
          shock_exclude = FALSE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot4

plot4
```

### Norway

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot5

plot5
```


### Peru

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 8, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot6

plot6
```

### Singapore

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

Modeling `r mh_categoryc[j]` for Singapore is not appropiate due to missing data in numerator.

```{r}
fake <- data.frame(x = seq(1, 48, 1), 
                   y = seq(1, 48, 1))

fake |> 
  ggplot(aes(x = x, y = y)) + 
  theme_void() + 
  annotate(geom = "text", 
           x = 24, 
           y = 24, 
           label = "Not calculable", 
           color = "black", 
           size = 6) -> plot7
```

### Sweden

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot8

plot8
```


### USA

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }

```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_usa(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot9

plot9
```
:::

#### Table

```{r}
# Cargar la biblioteca

tab_f <- tab |> 
  arrange(country, effect) |> 
  mutate(
    country_effect = if_else(effect == "Level change", country, NA_character_),
    effect = case_when(
      effect == "Level change" ~ "   Level change",
      effect == "Trend change" ~ "   Trend change"
    )
  ) |> 
  dplyr::select(-mh_category, -country) |> 
  dplyr::select(country_effect, effect, estimate)

# Crear la tabla flextable
ft <- flextable(tab_f)

# Cambiar los nombres de las columnas
ft <- set_header_labels(ft, 
                        country_effect = "Country",
                        effect = "Effect measure", 
                        estimate = "IRR (95%CI), p-value")

# Formatear la tabla
ft <- ft %>%
  align(align = "left") %>%
  padding(padding = 5) %>%
  fontsize(size = 11) %>%
  bold(part = "header") %>%
  bold(i = which(!is.na(tab_f$country_effect)), j = "country_effect") %>%
  autofit()

# Guardar como documento de Word
save_as_docx(ft, 
             path = here("table_effects", 
                         paste0("table_", mh_categoryc[j], ".docx")))

ft
```


#### Plot

```{r}
#| warning: false
#| message: false
((plot1 | plot2 | plot3) / 
  (plot4 | plot5 | plot6) / 
  (plot7 | plot8 | plot9)) + 
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A') & 
  theme(legend.position="bottom") -> plot_effect_final

ggsave(filename = paste0(mh_categoryc[j], ".png"), 
       plot = plot_effect_final, 
       device = "png", 
       path = here("img", "plot_effects"), 
       scale = 1.5, 
       width = 18, 
       height = 18, 
       units = "cm", 
       dpi = 900)
```

```{r}
knitr::include_graphics(here("img", 
                             "plot_effects", 
                             paste0(mh_categoryc[j], ".png")))
```



### **Outcome:** Bipolar, Schizophrenia and other Psycotic Disorders

::: {.panel-tabset}

### Countries

1. Argentina
2. Australia
3. Canada
4. China
5. Norway
6. Peru
7. Singapore
8. Sweden
9. USA

### Argentina

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1

if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 5, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot1

plot1
```

### Australia

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }

```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot2

plot2
```

### Canada

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot3

plot3
```

### China

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_china(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 2, q = 1, 
          data = mh_visits5b, 
          shock_exclude = FALSE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot4

plot4
```

### Norway

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot5

plot5
```


### Peru

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 8, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot6

plot6
```

### Singapore

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot7

plot7
```

### Sweden

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot8

plot8
```


### USA

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_usa(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot9

plot9
```

:::

#### Table

```{r}
# Cargar la biblioteca

tab_f <- tab |> 
  arrange(country, effect) |> 
  mutate(
    country_effect = if_else(effect == "Level change", country, NA_character_),
    effect = case_when(
      effect == "Level change" ~ "   Level change",
      effect == "Trend change" ~ "   Trend change"
    )
  ) |> 
  dplyr::select(-mh_category, -country) |> 
  dplyr::select(country_effect, effect, estimate)

# Crear la tabla flextable
ft <- flextable(tab_f)

# Cambiar los nombres de las columnas
ft <- set_header_labels(ft, 
                        country_effect = "Country",
                        effect = "Effect measure", 
                        estimate = "IRR (95%CI), p-value")

# Formatear la tabla
ft <- ft %>%
  align(align = "left") %>%
  padding(padding = 5) %>%
  fontsize(size = 11) %>%
  bold(part = "header") %>%
  bold(i = which(!is.na(tab_f$country_effect)), j = "country_effect") %>%
  autofit()

# Guardar como documento de Word
save_as_docx(ft, 
             path = here("table_effects", 
                         paste0("table_", mh_categoryc[j], ".docx")))

ft
```


#### Plot

```{r}
#| warning: false
#| message: false
((plot1 | plot2 | plot3) / 
  (plot4 | plot5 | plot6) / 
  (plot7 | plot8 | plot9)) + 
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A') & 
  theme(legend.position="bottom") -> plot_effect_final

ggsave(filename = paste0(mh_categoryc[j], ".png"), 
       plot = plot_effect_final, 
       device = "png", 
       path = here("img", "plot_effects"), 
       scale = 1.5, 
       width = 18, 
       height = 18, 
       units = "cm", 
       dpi = 900)
```

```{r}
knitr::include_graphics(here("img", 
                             "plot_effects", 
                             paste0(mh_categoryc[j], ".png")))
```



### **Outcome:** Dementia

::: {.panel-tabset}

### Countries

1. Argentina
2. Australia
3. Canada
4. China
5. Norway
6. Peru
7. Singapore
8. Sweden
9. USA

### Argentina

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1

if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 5, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot1

plot1
```

### Australia

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }

```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot2

plot2
```

### Canada

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot3

plot3
```


### China

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_china(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 2, q = 1, 
          data = mh_visits5b, 
          shock_exclude = FALSE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot4

plot4
```


### Norway

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot5

plot5
```


### Peru

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 8, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot6

plot6
```

### Singapore

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot7

plot7
```

### Sweden

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot8

plot8
```

### USA

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_usa(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot9

plot9
```

:::

#### Table

```{r}
# Cargar la biblioteca

tab_f <- tab |> 
  arrange(country, effect) |> 
  mutate(
    country_effect = if_else(effect == "Level change", country, NA_character_),
    effect = case_when(
      effect == "Level change" ~ "   Level change",
      effect == "Trend change" ~ "   Trend change"
    )
  ) |> 
  dplyr::select(-mh_category, -country) |> 
  dplyr::select(country_effect, effect, estimate)

# Crear la tabla flextable
ft <- flextable(tab_f)

# Cambiar los nombres de las columnas
ft <- set_header_labels(ft, 
                        country_effect = "Country",
                        effect = "Effect measure", 
                        estimate = "IRR (95%CI), p-value")

# Formatear la tabla
ft <- ft %>%
  align(align = "left") %>%
  padding(padding = 5) %>%
  fontsize(size = 11) %>%
  bold(part = "header") %>%
  bold(i = which(!is.na(tab_f$country_effect)), j = "country_effect") %>%
  autofit()

# Guardar como documento de Word
save_as_docx(ft, 
             path = here("table_effects", 
                         paste0("table_", mh_categoryc[j], ".docx")))

ft
```


#### Plot

```{r}
#| warning: false
#| message: false
((plot1 | plot2 | plot3) / 
  (plot4 | plot5 | plot6) / 
  (plot7 | plot8 | plot9)) + 
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A') & 
  theme(legend.position="bottom") -> plot_effect_final

ggsave(filename = paste0(mh_categoryc[j], ".png"), 
       plot = plot_effect_final, 
       device = "png", 
       path = here("img", "plot_effects"), 
       scale = 1.5, 
       width = 18, 
       height = 18, 
       units = "cm", 
       dpi = 900)
```

```{r}
knitr::include_graphics(here("img", 
                             "plot_effects", 
                             paste0(mh_categoryc[j], ".png")))
```



### **Outcome:** Sleep Disorders

::: {.panel-tabset}

### Countries

1. Argentina
2. Australia
3. Canada
4. China
5. Norway
6. Peru
7. Singapore
8. Sweden
9. USA

### Argentina

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1

if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 5, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot1

plot1
```

### Australia

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot2

plot2
```

### Canada

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot3

plot3
```

### China

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_china(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 2, q = 1, 
          data = mh_visits5b, 
          shock_exclude = FALSE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot4

plot4
```


### Norway

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot5

plot5
```


### Peru

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 8, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot6

plot6
```

### Singapore

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

Modeling `r mh_categoryc[j]` for Singapore is not appropiate due to missing data in numerator.

```{r}
fake <- data.frame(x = seq(1, 48, 1), 
                   y = seq(1, 48, 1))

fake |> 
  ggplot(aes(x = x, y = y)) + 
  theme_void() + 
  annotate(geom = "text", 
           x = 24, 
           y = 24, 
           label = "Not calculable", 
           color = "black", 
           size = 6) -> plot7
```

### Sweden

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot8

plot8
```

### USA

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_usa(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot9

plot9
```

:::

#### Table

```{r}
# Cargar la biblioteca

tab_f <- tab |> 
  arrange(country, effect) |> 
  mutate(
    country_effect = if_else(effect == "Level change", country, NA_character_),
    effect = case_when(
      effect == "Level change" ~ "   Level change",
      effect == "Trend change" ~ "   Trend change"
    )
  ) |> 
  dplyr::select(-mh_category, -country) |> 
  dplyr::select(country_effect, effect, estimate)

# Crear la tabla flextable
ft <- flextable(tab_f)

# Cambiar los nombres de las columnas
ft <- set_header_labels(ft, 
                        country_effect = "Country",
                        effect = "Effect measure", 
                        estimate = "IRR (95%CI), p-value")

# Formatear la tabla
ft <- ft %>%
  align(align = "left") %>%
  padding(padding = 5) %>%
  fontsize(size = 11) %>%
  bold(part = "header") %>%
  bold(i = which(!is.na(tab_f$country_effect)), j = "country_effect") %>%
  autofit()

# Guardar como documento de Word
save_as_docx(ft, 
             path = here("table_effects", 
                         paste0("table_", mh_categoryc[j], ".docx")))

ft
```


#### Plot

```{r}
#| warning: false
#| message: false
((plot1 | plot2 | plot3) / 
  (plot4 | plot5 | plot6) / 
  (plot7 | plot8 | plot9)) + 
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A') & 
  theme(legend.position="bottom") -> plot_effect_final

ggsave(filename = paste0(mh_categoryc[j], ".png"), 
       plot = plot_effect_final, 
       device = "png", 
       path = here("img", "plot_effects"), 
       scale = 1.5, 
       width = 18, 
       height = 18, 
       units = "cm", 
       dpi = 900)
```

```{r}
knitr::include_graphics(here("img", 
                             "plot_effects", 
                             paste0(mh_categoryc[j], ".png")))
```



### **Outcome:** Substance-Related and Addictive Disorders

::: {.panel-tabset}

### Countries

1. Argentina
2. Australia
3. Canada
4. China
5. Norway
6. Peru
7. Singapore
8. Sweden
9. USA

### Argentina

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1

if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 5, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot1

plot1
```

### Australia

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }

```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot2

plot2
```


### Canada

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot3

plot3
```


### China

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_china(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 2, q = 1, 
          data = mh_visits5b, 
          shock_exclude = FALSE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot4

plot4
```

### Norway

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot5

plot5
```


### Peru

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 8, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot6

plot6
```

### Singapore

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 11, q = 0, 
          data = mh_visits5b)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot7

plot7
```

### Sweden

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_norway(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 6, q = 0, 
          data = mh_visits5b, 
          shock_exclude = FALSE, 
          mean_cond = TRUE, 
          dum_outlier = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot8

plot8
```


### USA

```{r}
#| message: false
#| warning: false
# Set the counter
i <- i + 1
if (i %% 9 == 0) {
    j <- (i - 1) %/% 9 + 1
  } else {
    j <- i %/% 9 + 1
  }
```

- **Country:** `r countryc[i]`
- **Mental Health Category:** `r mh_categoryc[j]`

```{r}
# Model
mod_full <- sti_model_usa(country = countryc[i], 
          mh_category = mh_categoryc[j], 
          p = 1, q = 0, 
          data = mh_visits5b, 
          shock_exclude = TRUE)
```

- The autocorrelation function of residuals from a naive glm that does not account for autocorrelation is the following: 

```{r}
#| message: false
#| warning: false
mod_full$auto_plot; mod_full$arima
```

- The normalized residuasl from  a GLMMM that take into account dependence of residuls around the time shows no autocorrelation:

```{r}
#| message: false
#| warning: false
mod_full$dx.plot
```

The final model is the following: 

```{r}
summary(mod_full$mod)
```

```{r}
parameters::model_parameters(mod_full$mod) |> 
  dplyr::select(Parameter, Coefficient, CI_low, CI_high, p) |> 
  filter(Parameter %in% c("To", "To:I(time - tpand)")) |> 
  as_data_frame() |> 
  rename(est = Coefficient, 
         ll = CI_low, 
         ul = CI_high) |> 
  mutate(effect = c("Level change", "Trend change"), 
         across(c(est, ll, ul), ~(round(exp(.x) , 3))), 
         p = if_else(p < 0.001, "p < 0.001", 
                     as.character(paste0("p = ", round(p, 3)))), 
         estimate = str_glue("{est} ({ll} to {ul}), {p}"), 
         estimate = as.character(estimate), 
         mh_category = mh_categoryc[j], 
         country = countryc[i]
         ) |> 
  dplyr::select(country, mh_category, effect, estimate) -> tab0

tab <- tab0 |>
  bind_rows(tab)

tab |> 
  knitr::kable()
```

```{r}
#| warning: false
#| message: false
sti_effect_ploter(mod_full, 
                  alfa = alfa0,
                  alfa_ribbon = alfa_ribbon0,
                  color_point = color_point0, 
                  color_line = color_line0, 
                  color_ribbon_ex = color_ribbon_ex0,
                  color_ribbon_def = color_ribbon_def0, 
                  color_interrupt = color_interrupt0,
                  mindate = mindate0, 
                  maxdate = maxdate0) -> plot9

plot9
```

:::

#### Table

```{r}
# Cargar la biblioteca

tab_f <- tab |> 
  arrange(country, effect) |> 
  mutate(
    country_effect = if_else(effect == "Level change", country, NA_character_),
    effect = case_when(
      effect == "Level change" ~ "   Level change",
      effect == "Trend change" ~ "   Trend change"
    )
  ) |> 
  dplyr::select(-mh_category, -country) |> 
  dplyr::select(country_effect, effect, estimate)

# Crear la tabla flextable
ft <- flextable(tab_f)

# Cambiar los nombres de las columnas
ft <- set_header_labels(ft, 
                        country_effect = "Country",
                        effect = "Effect measure", 
                        estimate = "IRR (95%CI), p-value")

# Formatear la tabla
ft <- ft %>%
  align(align = "left") %>%
  padding(padding = 5) %>%
  fontsize(size = 11) %>%
  bold(part = "header") %>%
  bold(i = which(!is.na(tab_f$country_effect)), j = "country_effect") %>%
  autofit()

# Guardar como documento de Word
save_as_docx(ft, 
             path = here("table_effects", 
                         paste0("table_", mh_categoryc[j], ".docx")))

ft
```


#### Plot

```{r}
#| warning: false
#| message: false
((plot1 | plot2 | plot3) / 
  (plot4 | plot5 | plot6) / 
  (plot7 | plot8 | plot9)) + 
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A') & 
  theme(legend.position="bottom") -> plot_effect_final

ggsave(filename = paste0(mh_categoryc[j], ".png"), 
       plot = plot_effect_final, 
       device = "png", 
       path = here("img", "plot_effects"), 
       scale = 1.5, 
       width = 18, 
       height = 18, 
       units = "cm", 
       dpi = 900)
```

```{r}
knitr::include_graphics(here("img", 
                             "plot_effects", 
                             paste0(mh_categoryc[j], ".png")))
```

## Reproducibility Ticket

```{r}
sessionInfo()
```

